%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-red}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
% \photo[circle,noedge,left]{./examples/profile}
\name{Felipe S.}{Oliveira}
\position{Software Engineeer{\enskip\cdotp\enskip}Security Analyst}
\address{Campinas, SP, Brazil}

\mobile{(+55) 19 98278-6172}
\email{fesoliveira@outlook.com}
% \homepage{github.com/fesoliveira014}
\github{fesoliveira014}
\linkedin{fesoliveira}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \extrainfo{extra informations}

% \quote{``Be the change that you want to see in the world."}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {Company Recruitment Team}
  {Advanced Micro Devices Inc.}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for Software Engineer}
% How the letter is opened
\letteropening{Greetings,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
% \letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Felipe S. Oliveira~~~·~~~Cover Letter}
  {}

% Print the title with above letter informations
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

\lettersection{About Me}
I am a Software Security Analyst working at SIDI, a Samsung research institute in Brazil. I am working in the security analysis of Android and Tizen services and applications on Samsung flagship devices, as well of many of their web applications and services. I have a Bachelor's Degree with Honours in Computer Science from State University of Campinas (Unicamp), in Brazil, and I was a visiting student at University of Toronto for 2 semesters in 2014. I also have development experience from working with a smaller team at my previous position, where I was mostly working in BIOS and bootloaders in security related solutions.

\lettersection{Why ARM?}
ARM has been a paramount of innovation in the computer industry. It was ARM's processors that enabled the existence of most modern handheld and IoT devices, and they continue to bring new and exciting technologies to the market. More recently ARM has been pushing into the desktop and server markets, areas in much need of ARM's vision and insight. I also have great interest in other areas pursued by ARM, such as their mobile GPUs and IoT projects.

\lettersection{Why Me?}
For the past couple years I have worked in both Software Security Engineering and Analysis. Through these I am confident I have acquired many skills that make me an excellent fit for your positions in Low Level Software Engineering. When I commenced these jobs I had never had any experience with security or low level programming, so I had to learn these skills the hard way, which I did with efficiency and efficacy in order to fullfil my tasks. Through these new experiences I became confident in working with mission-critical code and systems. I embrace challenging tasks and I am eager and enthusiastic when working with and learning about new technologies. \\

AMD is a fantastic company and one of the pillars that helped shape the world of technology we live in today. I look forward to the opportunity of working in such a great company and I hope to hear from you soon.

\end{cvletter}

%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter informations
\makeletterclosing

\end{document}
