%-------------------------------------------------------------------------------
% SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}

%-------------------------------------------------------------------------------
% CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Systems Software Engineer} % Job title
    {SiDi (Samsung Institute for the Development of Informatics)} % Organization
    {Campinas, Brazil} % Location
    {May 2019 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {R\&D of trusted applications and systems for Samsung devices.}
        \item {Collaborated with members in remote offices on the design of trusted applications.}
        \item {Contributed to the Samsung Android Framework, implementing system services and drivers.}
        \item {Developed applications in constrained environments with limited resources (ARM TrustZone).}
        \item {Developed Android applications and SDKs.}
        % \item {Conducted R\&D on hardwares such as the Embedded Secure Element (eSE) in mobile phones.}
      \end{cvitems}
    }

  \cventry
    {Software Security Analyst} % Job title
    {SIDI (Samsung Institute for the Development of Informatics)} % Organization
    {Campinas, Brazil} % Location
    {May 2017 - Apr 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Performed security analysis in Android and Tizen services, device drivers and applications.}
        \item {Performed reverse engineering in Samsung proprietary code, static and dynamic analysis and design evaluation.}
        \item {Acted in leadership roles, assigning tasks and coordinating with members in remote offices.}
        \item {Took part in penetration testing several Samsung web applications and servers.}
        \item {Provided security consulting for internal projects and teams.}
        \item {Implemented tools in order to facilitate and automate several project related tasks.}
      \end{cvitems}
    }

  \cventry
    {Software Engineer} % Job title
    {Kryptus - Solutions in Information Security} % Organization
    {Campinas, Brazil} % Location
    {Sept. 2016 - May 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and implemented secure systems for both proprietary and third-party solutions.}
        \item {Mostly low-level systems, such as BIOS extensions, bootloaders and hard-drive cryptography.}
        \item {Worked on remote management tools to enable monitoring and maintenance of these systems.}
        \item {Development in C, x86 Assembly, Python 2 with Django and REST API}
      \end{cvitems}
    }

\cvsubsection{Other Relevant Experiences}

  \cventry
    {Intern Full-stack Developer} % Job title
    {Stoom - Solutions in E-Commerce} % Organization
    {Campinas, Brazil} % Location
    {May 2016 - Sept. 2017} % Date(s)
    {
      % \begin{cvitems} % Description(s) of tasks/responsibilities
      %   \item {Assisted designing and implementing the Stoom e-commerce platform, using Apache Struts and Spring frameworks.}
      %   \item {Full-stack development, working on designing and deployment of third-party projects.}
      % \end{cvitems}
    }

  \cventry
    {Intern Software Developer} % Job title
    {Big Data University} % Organization
    {Toronto, Canada} % Location
    {May 2014 - Sept. 2014} % Date(s)
    {
      % \begin{cvitems} % Description(s) of tasks/responsibilities
      %   \item {Developed showcase products for Bluemix (IBM Cloud)}
      %   \item {For summer project, developed a home surveillance system in NodeJS and Python on a Raspberry Pi, using Cloudant and Bluemix.}
      % \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}